MCC Predictions

### 2018-06-23 stats/ex3_comparisons.Rmd
updating model predictions
updating model comparison and predictions

library(tidyverse)
library(knitr)
library(ggthemes)
library(langcog)
library(rwebppl)
```

@@

pred <- predictions %>%
  group_by(Model,Experiment,Change,Alignment)%>%
  multi_boot_standard(col = "corr")

@@

```{r plot models and data}

ggplot(pd, 
       aes(x = Change, y = mean, fill = Alignment)) +
  geom_bar(stat="identity", position = position_dodge(), color = 'black') + 
  geom_hline(yintercept = 0.5, lty=2)+
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width = 0.9))+
  labs(x=" ",y="Proportion Choosing More Informative")+
  facet_grid(Experiment ~ Model)+
  theme_few(base_size = 12) + 
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
  ylim(0,1)

```{r plot comparing models}

library(ggpubr)

plot1 <- data.frame(pd$Experiment[pd$Model=="Data"],pd$mean[pd$Model=="Data"],pd$mean[pd$Model=="Prior only"],rep("Data vs Prior only",8))
names(plot1) = c("Experiment","Data","Model","Comp")
plot2 <- data.frame(pd$Experiment[pd$Model=="Data"],pd$mean[pd$Model=="Data"],pd$mean[pd$Model=="Full model"],rep("Data vs Full model",8))
names(plot2) = c("Experiment","Data","Model","Comp")

plot <- rbind(plot1,plot2)

ggplot(data = plot,aes(x = Model, y = Data, col = Comp)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.3)+
  geom_point()+
  coord_fixed()+
  xlim(0,1)+ylim(0,1)+
  facet_grid(~Comp)+
  stat_cor(method = "pearson", label.x = 0.4, label.y = 0.9)+
  geom_smooth(method = "lm", se = F, col = "black")+
  theme_few() + 
  guides(col = F)+
  scale_colour_solarized()

@@

var two_objects = [
{ shape: "triangle", id:1, location: 1},  
{ shape: "circle", id:1, location: 2}
]

@@

var model = function(){
   var noise = 0

@@

@@

@@

var model = function(){
   var priorExponent = uniformDrift({a: 0, b:5, width: 0.1})

@@

var model = function(){
   var priorExponent = uniformDrift({a: 0, b:5, width: 0.1})
   var noise = uniformDrift({a: 0, b:1, width: 0.1})

@@

allPriorProbs2 <- allPriorProbs

allPriorProbs2$priorProbs = list(
    c(0.0333333, 0.9666667), 
    c(0.9666667, 0.0333333),
    c(0.3583333, 0.6416667),
    c(0.6416667, 0.3583333),
    c(0.1666667, 0.8333333),
    c(0.8333333, 0.1666667),
    c(0.4083333, 0.5916667),
    c(0.5916667, 0.4083333))

@@

```{r predictions prior, include = FALSE}
bda0 <- webppl(
  program_code = paste(rsaUtils, rsaModel2, bdaModel.prior, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
)

## distribution of model predictions
posterior.predictive1 = bda0 %>%
  filter(!(Parameter %in% c("noise", "priorExponent"))) %>%
  separate(Parameter, into = c("Experiment", "Change", "Alignment"), sep="_")

prior.model <- posterior.predictive1 %>%
  mutate(Model="Prior Model",
         Adjustment = "Noise",
         Type = "Prior only")%>%
  group_by(Model,Adjustment,Type,Experiment,Change,Alignment) %>%
  summarise(mean = estimate_mode(value))

@@

```{r predictions rsa noise, include = FALSE}
bda <- webppl(
  program_code = paste(rsaUtils, rsaModel2, bdaModel.rsa.noise, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
)

@@

## Bayesian credible intervals

library(coda)

hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}

@@

```{r predictions prior noise, include = FALSE}
bda1 <- webppl(
  program_code = paste(rsaUtils, rsaModel2, bdaModel.prior.noise, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
)

@@

```{r predictions rsa regularized prior, include = FALSE}
bda2 <- webppl(
  program_code = paste(rsaUtils, rsaModel2, bdaModel.rsa.regularizedPrior, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
)

@@

```{r predictions prior regularized prior, include = FALSE}
bda3 <- webppl(
  program_code = paste(rsaUtils, rsaModel2, bdaModel.prior.regularizedPrior, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
)

@@

```{r predictions rsa noise regularized prior, include = FALSE}
bda4 <- webppl(
  program_code = paste(rsaUtils, rsaModel2, bdaModel.rsa.regularizedPrior.noise, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
)

@@

```{r predictions prior noise regularized prior, include = FALSE}
bda5 <- webppl(
  program_code = paste(rsaUtils, rsaModel2, bdaModel.prior.regularizedPrior.noise, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
)

@@

```{r}
## joining noisy model predictions with other predictions
no.adj.models <- pd %>%
  mutate(Type = ifelse(Model == "Full model","RSA",ifelse(Model == "Data","Data",ifelse(Model == "No prior","No Prior","Prior only"))),
         Adjustment = "None")

p.com <- bind_rows(
  noisy.rsa.model,
  noisy.prior.model,
  regPrior.rsa.model,
  regPrior.prior.model,
  noisy.regPrior.rsa.model,
  noisy.regPrior.prior.model,
  no.adj.models
  )

@@

p.com$Data = rep(pd$mean[pd$Model=="Data"],10)

@@

ggplot(data = plot.model,aes(x = mean, y = Data, col = Model)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.3)+
  geom_point()+
  facet_grid(Type~Adjustment)+
  coord_fixed()+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  stat_cor(method = "pearson", label.x = 0.4, label.y = 0.9)+
  geom_smooth(method = "lm", se = F, col = "black", size =0.4)+
  theme_few() + 
  guides(col = F)+
  scale_colour_solarized()

@@

  var priorExponent = uniformDrift({a: 0, b:5, width: 0.1})

@@

@@

  var priorExponent = uniformDrift({a: 0, b:5, width: 0.1})

@@

llh.rsa <- webppl(
  program_code = paste(rsaUtils, rsaModel2, rsa.loglikelihood, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 5000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "RSA")

llh.rsa.noise <- webppl(
  program_code = paste(rsaUtils, rsaModel2, rsa.noise.loglikelihood, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 5000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "RSA Noisy")

llh.rsa.regPrior <- webppl(
  program_code = paste(rsaUtils, rsaModel2, rsa.regPrior.loglikelihood, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 5000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "RSA Regularized")

llh.rsa.noise.regPrior <- webppl(
  program_code = paste(rsaUtils, rsaModel2, rsa.regularizedPrior.noise.loglikelihood, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 5000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "RSA Noisy Regularized")

@@

llh.prior <- webppl(
  program_code = paste(rsaUtils, rsaModel2, prior.loglikelihood, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 5000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "Prior only")

llh.prior.noise <- webppl(
  program_code = paste(rsaUtils, rsaModel2, prior.noise.loglikelihood, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 5000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "Prior only Noisy")

llh.prior.regPrior <- webppl(
  program_code = paste(rsaUtils, rsaModel2, prior.regPrior.loglikelihood, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 5000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "Prior only Regularized")

llh.prior.noise.regPrior <- webppl(
  program_code = paste(rsaUtils, rsaModel2, prior.regularizedPrior.noise.likelihood, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 5000),
  chains = 3, cores = 3
) %>%
  mutate(Model = "Prior only Noisy Regularized")

@@

likelihood_overview <- bind_rows(
  llh.rsa,
  llh.prior,
  llh.rsa.noise,
  llh.prior.noise,
  llh.prior.regPrior,
  llh.rsa.regPrior %>% filter(value != "-Infinity") %>% mutate(value = as.numeric(value)),
  llh.rsa.noise.regPrior,
  llh.prior.noise.regPrior)

ggplot(likelihood_overview, aes(x = value))+
  geom_histogram()+
  xlim(-700,-500)+
  facet_wrap(~Model, nrow = 2)

@@

```{r logsum summary}
library(matrixStats)

llh.plot <- likelihood_overview %>%
  group_by(Model)%>%
  summarize(logSumExp = logSumExp(value),
            max = max(value))%>%
  mutate(Model = reorder(Model,logSumExp))

ggplot(llh.plot, aes(x = Model, y = logSumExp, fill = Model))+
  geom_bar(stat="identity", color = "black")+
  ggtitle("logsumexp per model")+
  theme_few()+ 
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))

@@

@@

At what ratio does it flip back to more informative?

```{r , echo=FALSE}

pred <- data.frame(
  Prior = c("90/10","80/20","70/30","60/40","50/50"),
  corr = c(0.1118794400899893,0.24897738407515466,0.40911964439987003,0.5807810413750243,0.74)
)

ggplot(pred, 
       aes(x = Prior, y = corr, fill = Prior)) +
  geom_bar(stat="identity") + 
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Choosing More Informative")+
  theme_few(base_size = 12) +
  scale_fill_discrete(name = "Prior: less inf / more inf")+
  ylim(0,1)+
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())

>>>>

load("model.comparisons.RData")

library(tidyverse)
library(knitr)
library(ggthemes)
library(langcog)
library(rwebppl)
library(matrixStats)
library(coda)

hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
```

@@

pred2 <- predictions %>%
  group_by(Model,Experiment,Change,Alignment)%>%
  multi_boot_standard(col = "corr")

@@

@@

@@

@@

  return  [conditionInfo.Experiment + "_" + conditionInfo.Change + "_" +  conditionInfo.Alignment, Math.exp(priorOnlyPredictions.score(1))]

@@

 return extend(_.fromPairs(conditionOutput))
}
'
```

```{r bda model rsa, include = FALSE}
bdaModel.rsa <-'
var allConditions = dataFromR.allConditions
var allData = dataFromR.allData
var allPriorProbs = dataFromR.allPriorProbs

 return extend(_.fromPairs(conditionOutput))
}
'
```

@@

var model = function(){
   var priorExponent = uniformDrift({a: 0, b:3, width: 0.1})

@@

var model = function(){
   var priorExponent = uniformDrift({a: 0, b:3, width: 0.1})
   var noise = uniformDrift({a: 0, b:1, width: 0.1})

@@

@@

```{r predictions prior, include = FALSE}
bda_priorOnly <- webppl(
  program_code = paste(rsaUtils, rsaModel2, bdaModel.prior, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "MCMC", samples = 10000, burn = 2000, verbose = T)
)

prior.model <- bda_priorOnly %>%
  filter(!(Parameter %in% c("noise", "priorExponent"))) %>%
  separate(Parameter, into = c("Experiment", "Change", "Alignment"), sep="_")%>%
  mutate(Model="Prior Model",
         Adjustment = "None",
         Type = "Prior only")%>%
  group_by(Model,Adjustment,Type,Experiment,Change,Alignment) %>%
  summarise(mean = estimate_mode(value))

@@

```{r predictions rsa, include = FALSE}
bda_rsa <- webppl(
  program_code = paste(rsaUtils, rsaModel2, bdaModel.rsa, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "MCMC", samples = 10000, burn = 2000, verbose = T)
)

rsa.model <- bda_rsa %>%
  filter(!(Parameter %in% c("noise", "priorExponent"))) %>%
  separate(Parameter, into = c("Experiment", "Change", "Alignment"), sep="_") %>%
  mutate(Model="RSA Model",
         Adjustment = "None",
         Type = "RSA")%>%
  group_by(Model,Adjustment,Type,Experiment,Change,Alignment) %>%
  summarise(mean = estimate_mode(value))

```{r predictions rsa noise, include = FALSE}
bda <- webppl(
  program_code = paste(rsaUtils, rsaModel2, bdaModel.rsa.noise, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "MCMC", samples = 10000, burn = 2000, verbose = T)
)

@@

@@

```{r predictions prior noise, include = FALSE}
bda1 <- webppl(
  program_code = paste(rsaUtils, rsaModel2, bdaModel.prior.noise, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "MCMC", samples = 10000, burn = 2000, verbose = T)
)

@@

```{r predictions rsa regularized prior, include = FALSE}
bda2 <- webppl(
  program_code = paste(rsaUtils, rsaModel2, bdaModel.rsa.regularizedPrior, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "MCMC", samples = 10000, burn = 2000, verbose = T)
)

@@

```{r predictions prior regularized prior, include = FALSE}
bda3 <- webppl(
  program_code = paste(rsaUtils, rsaModel2, bdaModel.prior.regularizedPrior, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "MCMC", samples = 10000, burn = 2000, verbose = T)
)

@@

```{r predictions rsa noise regularized prior, include = FALSE}
bda4 <- webppl(
  program_code = paste(rsaUtils, rsaModel2, bdaModel.rsa.regularizedPrior.noise, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "MCMC", samples = 10000, burn = 2000, verbose = T)
)

@@

```{r predictions prior noise regularized prior, include = FALSE}
bda5 <- webppl(
  program_code = paste(rsaUtils, rsaModel2, bdaModel.prior.regularizedPrior.noise, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "MCMC", samples = 10000, burn = 2000, verbose = T)
)

@@

```{r}
## joining noisy model predictions with other predictions
no.adj.models <- pd %>%
  filter(Model != "Full model", Model != "Prior only")%>%
  mutate(Type = ifelse(Model == "Full model","RSA",ifelse(Model == "Data","Data",ifelse(Model == "No prior","No Prior","Prior only"))),
         Adjustment = "None")

p.com <- bind_rows(
  prior.model,
  rsa.model,
  noisy.rsa.model,
  noisy.prior.model,
  regPrior.rsa.model,
  regPrior.prior.model,
  noisy.regPrior.rsa.model,
  noisy.regPrior.prior.model,
  no.adj.models
  )

@@

p.com$Data = rep(pd$mean[pd$Model=="Data"],10)
p.com$Data_ci_low = rep(pd$ci_lower[pd$Model=="Data"],10)
p.com$Data_ci_up = rep(pd$ci_upper[pd$Model=="Data"],10)

@@

ggplot(data = plot.model,aes(x = mean, y = Data, col = Model)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.3)+
  geom_point()+
  geom_errorbar(aes(ymin = Data_ci_low, ymax = Data_ci_up),width = 0)+
  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0)+
  facet_grid(Type~Adjustment)+
  coord_fixed()+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  stat_cor(method = "pearson", label.x = 0.4, label.y = 0.9)+
  geom_smooth(method = "lm", se = F, col = "black", size =0.4)+
  theme_few() + 
  guides(col = F)+
  scale_colour_solarized()

@@

  var priorExponent = uniformDrift({a: 0, b:3, width: 0.1})

  var pe = []

@@

loglike == -Infinity ? display(priorExponent) : null

@@

  var priorExponent = uniformDrift({a: 0, b:3, width: 0.1})

@@

llh.rsa <- webppl(
  program_code = paste(rsaUtils, rsaModel2, rsa.loglikelihood, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 10000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "RSA")

llh.rsa.noise <- webppl(
  program_code = paste(rsaUtils, rsaModel2, rsa.noise.loglikelihood, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 10000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "RSA Noisy")

llh.rsa.regPrior <- webppl(
  program_code = paste(rsaUtils, rsaModel2, rsa.regPrior.loglikelihood, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 10000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "RSA Regularized")

llh.rsa.noise.regPrior <- webppl(
  program_code = paste(rsaUtils, rsaModel2, rsa.regularizedPrior.noise.loglikelihood, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 10000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "RSA Noisy Regularized")

@@

llh.prior <- webppl(
  program_code = paste(rsaUtils, rsaModel2, prior.loglikelihood, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 10000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "Prior only")

llh.prior.noise <- webppl(
  program_code = paste(rsaUtils, rsaModel2, prior.noise.loglikelihood, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 10000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "Prior only Noisy")

llh.prior.regPrior <- webppl(
  program_code = paste(rsaUtils, rsaModel2, prior.regPrior.loglikelihood, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 10000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "Prior only Regularized")

llh.prior.noise.regPrior <- webppl(
  program_code = paste(rsaUtils, rsaModel2, prior.regularizedPrior.noise.likelihood, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 10000),
  chains = 3, cores = 3
) %>%
  mutate(Model = "Prior only Noisy Regularized")

@@

likelihood_overview <- bind_rows(
  llh.rsa,
  llh.prior,
  llh.rsa.noise,
  llh.prior.noise,
  llh.rsa.regPrior,
  llh.prior.regPrior,
  llh.rsa.noise.regPrior,
  llh.prior.noise.regPrior)

ggplot(likelihood_overview, aes(x = value))+
  geom_histogram()+
  xlim(-200,0)+
  facet_wrap(~Model, nrow = 2, scales = "free")

@@

```{r logsum summary}
llh.plot <- likelihood_overview %>%
  group_by(Model)%>%
  summarize(logP = logSumExp(value))%>%
  mutate(Model = reorder(Model,logP))

ggplot(llh.plot, aes(x = Model, y = logP, fill = Model))+
  geom_bar(stat="identity", color = "black")+
  ggtitle("logsumexp per model")+
  theme_few()+ 
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
  guides(fill = F)

@@

```{r more iterations on rsa models}

llh.n.10k <- webppl(
  program_code = paste(rsaUtils, rsaModel2, rsa.noise.loglikelihood, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 10000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "RSA Noisy 10k")

llh.n.20k <- webppl(
  program_code = paste(rsaUtils, rsaModel2, rsa.noise.loglikelihood, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 20000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "RSA Noisy 20k")

llh.n.50k <- webppl(
  program_code = paste(rsaUtils, rsaModel2, rsa.noise.loglikelihood, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 50000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "RSA Noisy 50k")

llh.nr.10k <- webppl(
  program_code = paste(rsaUtils, rsaModel2, rsa.regularizedPrior.noise.loglikelihood, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 10000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "RSA Noisy Regularized 10k")

llh.nr.20k <- webppl(
  program_code = paste(rsaUtils, rsaModel2, rsa.regularizedPrior.noise.loglikelihood, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 20000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "RSA Noisy Regularized 20k")

llh.nr.50k <- webppl(
  program_code = paste(rsaUtils, rsaModel2, rsa.regularizedPrior.noise.loglikelihood, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 50000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "RSA Noisy Regularized 50k")

```{r}
rsa_overview <- bind_rows(
  llh.n.10k,
  llh.n.20k,
  llh.n.50k,
  llh.nr.10k,
  llh.nr.20k,
  llh.nr.50k)

rsa.llh.plot <- rsa_overview %>%
  group_by(Model)%>%
  summarize(logP = logSumExp(value))%>%
  mutate(Model = reorder(Model,logP))

ggplot(rsa.llh.plot, aes(x = Model, y = logP, fill = Model))+
  geom_bar(stat="identity", color = "black")+
  ggtitle("logsumexp by number of samples")+
  theme_few()+ 
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
  guides(fill = F)

@@
